\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2015-01-08 ex_ante.tex
finish ex_ante section (7). move one bit to to_do_list.

Focusing on the case of weak bindings (i.e. tariff caps), we see that, as long as governments want to restrain lobbying, relative to non-cooperative levels, trade agreements will do deliver this result even when ex-ante lobbying is possible. If a government wants to encourage political pressure, it may want to consider eschewing trade agreements, although the tradeoff is losing the ability to internalize the terms of trade externality. If a government wants to restrain political pressure, a trade agreement is doubly good.

@@

\vskip.2in
Compare to ex-ante lobbying \`{a} la MRC.
\begin{itemize}
	\item Cooperative bargaining soln (maximize joint welfare of both governments and both lobbies) instead of extensive form
		\begin{itemize}
			\item leads to bizarre outcome where government will take into account lobby's profits even if $e^{\text{EA}}=0$.
		\end{itemize}
	\item In MRC main treatment, assume lobby has all the bargaining power
		\begin{itemize}
			\item Implies tariff caps and strong bindings equivalent, even though these split the surplus in very different ways. All surplus goes to lobby
			\item In the part that is only in the NBER working paper, they have
				\begin{itemize}
					\item $z=0$ (perfectly immobile capital)
					\item no ex-ante lobbying
					\item government has all the bargaining power
					\item government sometimes chooses free trade---so there IS an incentive to use the trade agreement as a domestic commitment device
				\end{itemize}
			\end{itemize}
	\item In MRC, no matter how tariff is set (cooperatively or non-cooperatively), contribution is $xp(\ov{t})$
		\begin{itemize}
			\item Not true in GH95
			\item In my set-up, lobby's incentives change when tariff-setting process changes
		\end{itemize}
	\item In MRC, weight on lobby's profits is $1+a$ no matter what. Doesn't vary in lobby's efforts. GH not really microfoundations for flexible model as in Long and Vousden (1991) / Baldwin (1987) model; microfoundations for more restrictive version with fixed weights; then decide $\tau$ to change PS, CS, etc. (p. 481 GH94). Can't get shocks as in this literature
		\begin{itemize}
			\item I still don't know exactly why you never want to reign in lobbying in GH; because it's just a conduit for information, and gov't is fully compensated for loss? But is it?
		\end{itemize}
\end{itemize}

>>>>

This contrasts with \Textcite{mrc2007}. In their model, which also features endogenous political pressure with ex-ante lobbying, tariff caps and exact tariff commitments are equivalent in the case of perfectly immobile capital. This seems to be the result of their assumption, within the context of a cooperative bargaining solution for the trade agreement phase, that the lobby has all the bargaining power and thus receives all rents. Because the lobby receives protection ex post without exerting effort under exact tariff commitments, these two types of bindings lead to very different decisions ex-ante and splits of the surplus ex-post in the model under consideration here.\footnote{One reason the lobby is not included in the cooperative bargaining formulation here is that it leads to the strange outcome that the governments overweight the lobby's profits even when the lobby exerts no effort ex ante.}

Focusing on the case of weak bindings (i.e. tariff caps), we see that, as long as governments want to restrain lobbying, relative to non-cooperative levels, trade agreements will deliver this result even when ex-ante lobbying is possible. If a government wants to encourage political pressure, it may want to consider eschewing trade agreements, although the tradeoff is losing the ability to internalize the terms of trade externality. If a government wants to restrain political pressure, a trade agreement is doubly good.

@@

### 2015-01-08 to_do_list.tex
update section 5 calculations, graphs and text (non-interior soln implications)
finish ex_ante section (7). move one bit to to_do_list.

\vskip.2in
\begin{itemize}
	\item Need to convey the possibilities of this set-up for capturing the real life dynamics of shocks integrated with lobbying dynamics, how that interacts with enforcement and administered protection
	\item Supply air tight argument / reference about $C+aW$ being equivalent to $\ga$ increasing everywhere
		\begin{itemize}
			\item CAN'T! It's not true! Only microfound a version with $1+a$ on those who lobby, $a$ on those who don't
		\end{itemize}
	\item perhaps re-emphasize that gov't can't completely control lobbying: can't make it higher than lobby's optimal. But this is b/c there's only one lobby
	\item finish escape clause result
	\item pg. 24 calculations
		\begin{itemize}
			\item Decide where political objective fcn. section goes now
		\end{itemize}
	\item re-write intro
		\begin{itemize}
			\item MRC-style results survive incorporation of ex-ante lobbying. TA still works to restrict lobbying in many cases, but also to keep lobbyists ``in the game''
			\item Baldwin-style gov't welfare function works for a set of questions, but not for this one
				\begin{itemize}
					\item Need to be able to say which predictions/design questions are okay: those that don't change lobbying incentives
				\end{itemize}
			\item Coates and Ludema (2001)---endogenous (add to list of GH, MRC)
			\item How do I want to sell the paper? In relation to what literature? (what lit does endogenous? what lit doesn't?)
			\item What if the WTO actually \textit{did} what the literature says it does? It wouldn't work
			\item Be more explicit about relationship between $\ga(e)$ and $\ga(s)$
		\end{itemize}
\end{itemize}

>>>>

\vskip.2in
\begin{itemize}
	\item Need to convey the possibilities of this set-up for capturing the real life dynamics of shocks integrated with lobbying dynamics, how that interacts with enforcement and administered protection
	\item Supply air tight argument / reference about $C+aW$ being equivalent to $\ga$ increasing everywhere
		\begin{itemize}
			\item CAN'T! It's not true! Only microfound a version with $1+a$ on those who lobby, $a$ on those who don't
		\end{itemize}
	\item perhaps re-emphasize that gov't can't completely control lobbying: can't make it higher than lobby's optimal. But this is b/c there's only one lobby
	\item finish escape clause result
	\item re-write intro
		\begin{itemize}
			\item MRC-style results survive incorporation of ex-ante lobbying. TA still works to restrict lobbying in many cases, but also to keep lobbyists ``in the game''
			\item Baldwin-style gov't welfare function works for a set of questions, but not for this one
				\begin{itemize}
					\item Need to be able to say which predictions/design questions are okay: those that don't change lobbying incentives
				\end{itemize}
			\item In MRC, weight on lobby's profits is $1+a$ no matter what. Doesn't vary in lobby's efforts. GH not really microfoundations for flexible model as in Long and Vousden (1991) / Baldwin (1987) model; microfoundations for more restrictive version with fixed weights; then decide $\tau$ to change PS, CS, etc. (p. 481 GH94). Can't get shocks as in this literature
			\item Coates and Ludema (2001)---endogenous (add to list of GH, MRC)
			\item How do I want to sell the paper? In relation to what literature? (what lit does endogenous? what lit doesn't?)
			\item What if the WTO actually \textit{did} what the literature says it does? It wouldn't work
			\item Be more explicit about relationship between $\ga(e)$ and $\ga(s)$
		\end{itemize}
\end{itemize}
